\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-07-10 paper.tex
[IROS review] various minor improvements

Our execution controllers rely on symbolic task planning to convert faraway
desires into a succession of atomic actions. We use in our architecture the
HATP planner (for Human Aware Task Planner~\cite{Alili2009}).  HATP is based on
a Hierarchical Task Network (HTN) refinement, which performs an iterative task
decomposition into sub-tasks until reaching atomic actions.  The \emph{planning
domain} defines the set of methods describing how to decompose a task and can
be seen as the procedural knowledge of the robot.

@@

Second remark, after some research (see appendix B of~\cite{Lemaignan2012a} for
a detailed discussion)  we have decided not to represent neither the planning
domain nor the resulting plans in the knowledge base: the planning domain (with
tasks pre- and postconditions) is stored in a specific format, outside of the
knowledge repository, and the plans are directly communicated to the robot
controller. From our experience, the OWL formalism is not a satisfying
representation language for concepts that are both tightly bound to time
representation and non-monotonic.

@@

\subsection{Cognitive load}

Fig.~\ref{fig|cognitiveload} is a plot of the log of interactions between the
robot modules and the knowledge base during a one-hour long experiment. Because
most of the communication between modules goes in fact through the knowledge
base in our architecture (Fig.~\ref{fig|archi}), it actually pictures the
intensity of internal information exchanges between the different deliberative
component of the robot over time. Since communication actually relies on
grounded semantic information, we can call this level of interaction the
\emph{cognitive load} of the robot.

This simplistic measurement needs to be refined to take into account the fact
that the raw number of RPC calls to the knowledge base only imperfectly
reflects the actual cognitive processes running on, but it opens interesting
perspective nevertheless. It would be interesting for example to compare
and look for correlations with the cognitive load of a human partner (measured
via EEG or qualitative feedback).

@@

>>>>

Our execution controllers rely on symbolic task planning to convert faraway
desires into a succession of atomic actions. We use in our architecture the
HATP planner (for Human Aware Task Planner~\cite{Alili2009}).  HATP is based on
a Hierarchical Task Network (HTN) refinement, which performs an iterative task
decomposition into sub-tasks until reaching atomic actions. The \emph{planning
domain} defines the set of methods describing how to decompose a task and
represents the procedural knowledge of the robot.

@@

Second remark, after some research (see appendix B of~\cite{Lemaignan2012a} for
a detailed discussion)  we have decided not to represent neither the planning
domain nor the resulting plans in the knowledge base: the planning domain (with
tasks pre- and postconditions) is stored in a specific format, outside of the
central declarative knowledge repository, and the plans are directly
communicated to the robot controller. Thus, like many other cognitive
architectures, we have independent declarative and procedural knowledge stores.

@@

@@

\subsection{Cognitive activity}

Fig.~\ref{fig|cognitiveload} is a plot of the interactions (knowledge
alterations or knowledge queries) between the robot's modules and the central
knowledge base during a one-hour long experiment. Because most of the
communication between modules are in fact supported by the knowledge base in
our architecture (Fig.~\ref{fig|archi}), it reflects well the exchanges of
semantic informations within the deliberative layer of the robot, which we can
tentatively call the \emph{cognitive activity} of the robot.

This simplistic measurement needs to be refined to take into account the fact
that the raw number of RPC calls to the knowledge base only imperfectly
reflects the actual cognitive processes running on, but it opens interesting
perspectives nevertheless. We could for instance investigate possible
correlations with the cognitive activity of a human partner (measured via EEG
or qualitative feedback).
